\documentclass{article}
\textheight=8.5in
\textwidth=6.5in
\oddsidemargin=0.0in
\topmargin=0.0in





\renewcommand\baselinestretch{1.0}           % single space
\pagestyle{empty}                            % no headers and page numbers
\oddsidemargin -10 true pt      % Left margin on odd-numbered pages.
\evensidemargin 10 true pt      % Left margin on even-numbered pages.
\marginparwidth 0.75 true in    % Width of marginal notes.
\oddsidemargin  0 true in       % Note that \oddsidemargin=\evensidemargin
\evensidemargin 0 true in
\topmargin -0.75 true in        % Nominal distance from top of page to top of\textheight 9.5 true in         % Height of text (including footnotes and figures)
\textwidth 6.375 true in        % Width of text line.
\parindent=0pt                  % Do not indent paragraphs
\parskip=0.15 true in
\usepackage{color}              % Need the color package



\begin{document}
\begin{center}
\section*{\underline{Instructor Phase Component Diagram}}
                               Author : Awadhesh Kumar Trivedi      
\end{center}
	\subsection*{\underline{Adding Student}}
\begin{enumerate}	
\item Request for registration of student in a particular course.

	\item Check student's existance in a particular Course.
\begin{itemize}
	\item If yes then send an error message that no duplicate entry allowed.

                     *(check conditions) 
	\item Else register student in a particular course and send a success message that 

        	student has been registered successfully.
\end{itemize}
\begin{center}        
\input{Inst_Adding_Student.latex}
\end{center}
\end{enumerate}
\subsection*{\underline{Modify student's profile}}
\begin{enumerate}
	\item Request to edit student's profile.

	\item Update all the tables related to the particular student.

	\item Success message send that profile has been Updated.

\begin{center}
\input{Inst_Modify_profile.latex}
\end{center}
\end{enumerate}
\subsection*{\underline{Remove Student's role from his course}}
\begin{enumerate}
	\item Send the student name for remove of it's role.
   
	\item Check, if student exit in particular course.
    \begin{itemize}
	\item If yes, remove the role of student from particular course and send appropriate message.

	\item Else send an error message that student does not exit in particular course.
    \end{itemize}

\begin{center}
\input{Inst_RemovestudentRole.latex}
\end{center}
\end{enumerate}

	\subsection*{\underline{Send notice to users of course}}
 Request by Instructor to send the notice to all the instructors students registered on the server

	      parameters passed: 

			 role  = Instructor/student,notice text sender-id.

		         group = All,expiry time,notice-Readline[call Notice Management send notice]

	 Send the notice to all tha Instructors/Students.
\begin{center}
\input{Inst_Sendnotice_a.latex}
\end{center}

	 Return the appropriate message depending on whether step(2)is successful or not.

 Request by the admin to send the notice to all the Instructors/Students of a specific group/groups 

		[call Notice Management send Notice()]

	      parameters passed:

		         role  = Instructor/student,notice text,sender-id.

	          	 group = single group name/list of group names,expiry time,notice \& Readline.
\begin{center}
\input{Inst_Sendnotice_b.latex}
\end{center}

	 Send the notice to all the Instructors/Students of a specific group/groups.
	 Return the appropriate message depending whether  step(2)is successful or not.

\subsection*{\underline{Personal Message}}
\begin{enumerate}
	\item Request by instructor to send mail.

	\item Send the local mail to specific user.

	\item Return the appropriate message.
\begin{center}
\input{Inst_PersonalMessage.latex}
\end{center}
\end{enumerate}
\subsection*{\underline{Delete Notice}}
\begin{enumerate}
    \item
\begin{itemize}
 Request by the user to delete the selected notices posted by instructor himself.

		  [Call Notice Managment delete Notice()]

             parameters passed: notice-id of notices selected for deletion.

    Delete the notice passed in step(1)from the database.
    Return the appropriate message.
\begin{center}
\input{Inst_DeleteNoticeA.latex}
\end{center}
\end{itemize}
    \item
\begin{itemize}
    Request by the user to delete slected notice posted by a specific user.
    Delete the notice passed in step(1)from the database.
    Return the appropriate message.
\begin{center}
\input{Inst_DeleteNoticeB.latex}
\end{center}
\end{itemize}
\end{enumerate}

\subsection*{\underline{View All Students}}
\begin{enumerate}
	\item Requesting for user list.
	\item Retrieve either all user's list or list of users in specific course.
	\item Either return a vector of user details or show suitable error message.
\begin{center}
\input{Inst_Viewall_student.latex}
\end{center}
\end{enumerate}
\subsection*{\underline{Post general as well as course specific news}}
\begin{enumerate}
\item Request for general or course specific news.
\item If news posted  successfully,returns a suitable message.
\item Else return an error message.\\
         Parameter: Publish date,Sender id, group id, news subject,News details, Expiry time, course id.
\begin{center}
\input{Inst_Postgenral.latex}
\end{center}
\end{enumerate}
\subsection*{\underline{Modify or remove the news}}
\begin{enumerate}
	\item Request for modify/remove the news.
	\item If news modify/remove then return an appropriate message.
	\item Else return an error message.\\
        	Parameter:  Remove- News-id, user-id, group-id, course-id.
       	    Modify: Publish date, sender-id, group-id , course-id , News subject, News detail, Expiry time.
\begin{center}
\input{Inst_ModifyorRemove.latex}
\end{center}
\end{enumerate}
\subsection*{\underline{Maintain personalised and course specific diary}}
\begin{enumerate}
	\item Request sends for personal/course specific events.
	\item It will check for the day(time) for personal and course specific events.
	    		\item If there is no conflict between personal and course calendar time, it will send an appropriate message.
		\item Else it will return an error message.\\
			            Parameters:\\  
					Personal-Date, Details into, Expiry, End time,start time.\\
				        Course- Group-id, date, Detail info, Expiry, End time,start time.\\
	\end{enumerate}

\subsection*{\underline{Manage his personal routine task}}
\begin{enumerate}
	\item Request sends for new task.
	\item It will check the timing for the same day.
	\begin{itemize}
		\item if there is no conflict between new and earlier time. then it will send an appropriate message.

		        Parameters: user-id, title, End date, start date.
	\end{itemize}

\begin{center}
\input{Inst_Managehis_Personal.latex}
\end{center}
\end{enumerate}

\subsection*{\underline{Modify profile}}
\begin{enumerate}
	\item Sending request for editing profile.
	\item checks for the fields.
	   \begin{itemize}
		\item If there is any error message, it will return it.
		\item Else it will return appropriate message.

			       parameters: user-id, Question-id, Answer-id, List configuration, photo, First name Last name, Email-id.
	    \end{itemize}
\begin{center}
\input{Inst_Modify_profile.latex}
\end{center}
\end{enumerate}

\subsection*{\underline{Upload course content}}
\begin{enumerate}


	\item Sending request for the upload of the course content.
	\item Check for the filed or directory.
	\item Return the appropriate message.

        	 Parameters- course id, file name,topic name.

\begin{center}
\input{Inst_Upload_CourseContent.latex}
\end{center}
\end{enumerate}

\subsection*{\underline{Publish or unpublish}}
\begin{enumerate}
	\item  Sending request to publish/unpublish course content.
	\item  Check for the file name and directory.
	    \begin{itemize}
		\item If its having '+' special character, it will return an error message.
		\item Else it will send an appropriate message.
	     \end{itemize}
                 Parameters: course-id, file name, topic name.
\begin{center}
\input{Inst_Publishor_unpublish.latex}
\end{center}
\end{enumerate}

\subsection*{\underline{Change the sequence of topics}}
\begin{enumerate}
        \item Send request to change the sequence of topics.
	\item It will return the appropriate message.

\begin{center}
\input{Inst_Change.latex}
\end{center}
\end{enumerate}

\subsection*{\underline{Enable or Disable guest facility}}
\begin{enumerate}


	\item Sending request to enable/disable guest login facility.
	\item It will return appropriate message.

	              Parameters: course-id, user-id.

\begin{center}
\input{Inst_EnaleorDisableguestF.latex}
\end{center}
\end{enumerate}
\subsection*{\underline{Can update and view the marks}}
\begin{enumerate}	
	\item Sending request to upload/view marks.
	\item Return the appropriate message.

              Parameters: course-id, user-id, marks.
\end{enumerate}
\subsection*{\underline{Download the list of students}}
\begin{enumerate}
	\item Sending request for download the list of students.
	\item Return the appropriate message.
\begin{center}
\input{Inst_Downloadthelistofstudent.latex}
\end{center}
\end{enumerate}

\subsection*{\underline{Backup of Course Content and Discussion Board/restoring the same}}
\begin{enumerate}
\item Sending request.
	\item Getting the appropriate message.

\end{enumerate}

\subsection*{\underline{Change password}}
\begin{enumerate}

\item Sending request to change password.
	\item It will check whether user exits or not.
	     \begin{itemize}
			\item If user does not exist,will return an error message.
			 \item Else it will ask for answer of list question.
				\begin{itemize}
					\item If answer doesnot match, it will return an error message.
					\item Else it return the sussessful message.
				
						 Parameter: User-id, Question-id, Answer, Old password, New password.
				 \end{itemize}
		\end{itemize}


\begin{center}
\input{Inst_Changepassword.latex}
\end{center}
\end{enumerate}
\subsection*{\underline{Generate Question Bank}}
\begin{enumerate}
	\item Sending request to generate question.
	\item It returns the appropriate message.
\begin{center}   
\input{Inst_Generate_QB.latex}
\end{center}
\end{enumerate}
\subsection*{\underline{Generate Quiz from existing Q.B.S}}
\begin{enumerate}
	\item Sending request to generate quiz.
	\item It return the appropriate message.
\begin{center}
\input{Inst_GenerateQuiz_existing.latex}
\end{center}
\end{enumerate}
\subsection*{\underline{Login into the Chat Sender}}
\begin{enumerate}
\item Sending request to login into Chat Server.
\item It returns the appropriate message.

\begin{center}
\input{Inst_LoginintotheChatesender.latex}
\end{center}
\end{enumerate}

Written by :- Rekha Pal
\end{document}
