\documentclass{article}
\usepackage{graphicx}
\textheight=8.5in
\textwidth=6.5in
\oddsidemargin=0.0in
\topmargin=0.0in



\renewcommand\baselinestretch{1.0}           % single space
\pagestyle{empty}                            % no headers and page numbers
\oddsidemargin -10 true pt      % Left margin on odd-numbered pages.
\evensidemargin 10 true pt      % Left margin on even-numbered pages.
\marginparwidth 0.75 true in    % Width of marginal notes.
\oddsidemargin  0 true in       % Note that \oddsidemargin=\evensidemargin
\evensidemargin 0 true in
\topmargin -0.75 true in        % Nominal distance from top of page to top of\textheight 9.5 true in         % Height of text (including footnotes and figures)
\textwidth 6.375 true in        % Width of text line.
\parindent=0pt                  % Do not indent paragraphs
\parskip=0.15 true in
\usepackage{color}              % Need the color package
\usepackage{epsfig}


\begin{document}
\begin{center}

\section*{\underline{DEFINE REPOSITORY}}
              Author Name : Mithelesh Parihar \& Vartika Nigam
\end{center}
\begin{enumerate}
\item Define a repository.
\item Generating ACL so that user getting repository has e/w permission.
\item Success/failure message.
\begin{center}
\input{definerepQ.B.latex}
\end{center}
\end{enumerate}
\subsection*{\underline{DEFINE A MODULE IN REPOSITORY}}
\begin{enumerate}
\item Define a module in repository.
\item Request for creation of module.
\item Access right for repository checked for user.
\item If fails the send message permission denied.
\item Module creation message success/failure.

\input{definerep_Q.B.latex}
\end{enumerate}
\subsection*{\underline{Adding a question to a module in repository}}
\begin{enumerate}
\item User interact with web application. 
\item User request to insert a question. 
\item Check all for authorization and permission. 
\item Success/failure message to user. 
\item If success, user select type of question. 
\item Insert the question and submit. 
\item Check the ACL permission. 
\item Put the question in repository (module). 
\item Notify the message for the confirmation. 
\end{enumerate}
\subsection*{\underline{Getting repository list}}
\begin{enumerate}
\item User interact with web application. 
\item Send the request by user.  
\item Check the ACL control for right user. 
\item Failure message to user. 
\item It success enter to the Q.B.R with user id and request for list. 
\item Get the list of repository.(response from Q.B.R). 
\item Check the ACL for user's repository(it invoke any other action). 
\item Display the list to user.
\input{GettingrepQB.latex}
\end{enumerate}
\subsection*{\underline{Select a module}}
\begin{enumerate}
\item User interact with web application. 
\item Send the request for listing of modules. 
\item Check the ACL for right user. 
\item Failure message to user. 
\item If the right use get the list of all modules. 
\item Display the list to user. 
\item Select a module.

\begin{center}
\input{selectamodule.latex}
\label{figure:SELECT A MODULE}
\end{center}
\end{enumerate}
\subsection*{\underline{Getting a question from repository}}
\begin{enumerate}
\item Request to view the question. 
\item User request. 
\item Check ACL for permission (R/W/ACC....) 
\item success/failure message. 
\item If success inter into Q.B. 
\item Return list of question in module. 
\item Select a question which user want. 
\item ACL check and pass the question-id. 
\item Pass request to display the question. 
\item Return question to user.

\begin{center}
\input{gettingaquestionfrom.latex}
\label{figure:GETTING A QUESTION FROM REPOSITORY}
\end{center}
\end{enumerate}

\subsection*{\underline{Editing a question and save in repository}}
\begin{enumerate}
\item Interact with web application. 
\item Select a module for edit the question. 
\item Check the user permission for editing of the question. 
\item It failure message to the user. 
\item It success then get the detail of the selected question. 
\item Modify the question. 
\item Save the changer. 
\item Message to user for success of changes.

\begin{center}
\input{editingaquestion.latex}
\label{figure:EDITING A QUESTION AND SAVE IN REPOSITORY}
\end{center}
 \end{enumerate}

\subsection*{\underline{Deleting a repository}}
\begin{enumerate}
\item User interact with the web application. 
\item Sent the deletion request. 
\item Check the ACL for deletion permission. 
\item It failure then message to user. 
\item It success then match the Q.B.R and delete the repository. 
\item Success message of deletion to use.
\begin{center}
\input{deletingarep.latex}
\label{figure:deletingarep.latex}
\end{center}
\end{enumerate}
\subsection*{\underline{Deleting a module}}
\begin{enumerate}
\item User interact with web application. 
\item Sending the request for deleting module by user. 
\item Check the authorization for deletion. 
\item Failure message to user. 
\item If success delete the selected module. 
\item Success deletion message to user. 
\input{deletingamodule.latex}
\label{figure:deletingamodule.latex}
\end{enumerate}

\subsection*{\underline{Deleting a question in a module}}
\begin{enumerate}
\item User interact with web application. 
\item Request for deletion of question. 
\item Check the ACL for permission. 
\item It fail then message to use. 
\item It success select to question from the list for deletion. 
\item Check the ACL for permission of question deletion. 
\item It failure message to user. 
\item It success the delete the question. 
\item Deletion message to user. 
\begin{center}
\input{Delete_Quiz.latex}
\label{figure:Delete_Quiz.latex}
\end{center}
\end{enumerate}

\subsection*{\underline{Editing module properties}} 
\begin{enumerate}
\item User interact with web application. 
\item Send request to get the properties of repository. 
\item check ACL for right author to change the repository properties. 
\item On failure message to user. 
\item If success get the properties for the repository from Q.B. 
\item Change the properties of selected repository. 
\item Check the ACL if not permitted send user bank. 
\item If permitted save properties. 
\item Success message for response.
\begin{center}
\input{editingmodulepro.latex}
\end{center}
\end{enumerate}

\subsection*{\underline{Search the module in which question with a question}} 
\begin{enumerate}
\item User interact with web application. 
\item Send a keyword with the request to search a module. 
\item Check the ACL for search permission. 
\item It fail message to use. 
\item It success the send request in Q.B.R with keyword. 
\item Get all the list of module in which question with keyword. 
\item Check the ACL for read permission. 
\item Display list to user.
\begin{center}
\input{searchthemodulein.latex}
\label{figure:searchthemodulein.latex}
\end{center}
\end{enumerate}

\subsection*{\underline{Search the question in the repository with a key word}}
\begin{enumerate}
\item User interact with the web application. 
\item Send the keyword for searching the question. 
\item Check the ACL for searching. 
\item It file then message to user. 
\item It success then pass the keyword in Q.B.R. 
\item Get all the question which related with the keyword from every dual. 
\item Check the read permission for every question. 
\item Display the question to user.
\begin{center}
\input{searchthequestionintherep.latex}
\label{figure:searchthequestionintherep.latex}
\end{center}
\end{enumerate}

                                             Written by :- Rekha Pal  
\end{document}
