\documentclass{article}
\usepackage{graphicx}
\textheight=8.5in
\textwidth=6.5in
\oddsidemargin=0.0in
 
 
\renewcommand\baselinestretch{1.0}           % single space
\pagestyle{empty}                            % no headers and page numbers
\oddsidemargin -10 true pt      % Left margin on odd-numbered pages.
\evensidemargin 10 true pt      % Left margin on even-numbered pages.
\marginparwidth 0.75 true in    % Width of marginal notes.
\oddsidemargin  0 true in       % Note that \oddsidemargin=\evensidemargin
\evensidemargin 0 true in
\topmargin -0.75 true in        % Nominal distance from top of page to top of\textheight 9.5 true in         % Height of text (including footnotes and figures)
\textwidth 6.375 true in        % Width of text line.
\parindent=0pt                  % Do not indent paragraphs
\parskip=0.15 true in
\usepackage{color}              % Need the color package
\usepackage{psfig}
 
\begin{document}
\begin{center}
\section*{\underline{Check Registration}}
\end{center}
\begin{enumerate}
\item User send Check Registration request to Load Server.
\item Local Server tries to connect remote server Checks.
\item If connection not estableshed or Brihaspati Server not found/not running display message stop further action.
\item Local Server now connect to load database further all enter and password MDS.
\item Local Server sends this data to Remote Sender.
\item Remote Server sends to request Remote Database and matches Records.
\item Remote Server sends to request Remote Database and matches Records.
\item Remote Sender sends response to Local server.
\item Local server Sends message to client.
\end{enumerate}
\begin{center}
\input{checkreg.latex}
\label{figure:Checkreg.latex}
\end{center}
\subsection*{\underline{Get Course}}
It is Divided into Submodules.\\
Get course Content (single file).\\
Get course List.\\
\begin{enumerate}
\item User sends get course list to local server.
\item Local sender checks if transaction is for buy/sell.
\item If sell return.
\item If buy then check if data exits in Local(dataone)
\item If not return.
\item Check if course is expired.
\item If not return.
\item Check remote registration.
\item Sends request to remote server to get remote course list.
\item Local sever sends remote checks of file on remote server.
\end{enumerate}
\subsubsection*{\underline{Get Course Content(Single file)}}
\begin{enumerate}
\item User sends Get single file contents request to Local server.
\item Local server performs Get Course list.
\item Local server sends MDS of
       secretkey+client URL+ServerURL+sourse+Source Location properly+sourse file name+destination Location properly+destination file name+Remote server.
\item Remote Server makes its own MDS key and match with Local server MDS key.
\item If Match not found return not Authorized.
\item If match found return the file contents to Local server.
\item Local server save into properly the system and make entries in xml file.
\end{enumerate}
\begin{center}
\input{GetContent.latex}
\label{figure:GetContent.latex}
\end{center}
\subsection*{\underline{View Course}}
\begin{enumerate}
\item User Checks on view file link.
\item Local server now see if lost file fetched war with 24 hourse.
\item If with 24 hours file --- from local server.
\item If not return ge single file content.
\begin{center}
\input{Viewcheck.latex}
\label{figure:Viewcheck.latex}
\end{center}
\end{enumerate}
\end{document}
