\documentclass{article}
\usepackage{graphicx}
\textheight=8.5in
\textwidth=6.5in
\oddsidemargin=0.0in
 

\renewcommand\baselinestretch{1.0}           % single space
\pagestyle{empty}                            % no headers and page numbers
\oddsidemargin -10 true pt      % Left margin on odd-numbered pages.
\evensidemargin 10 true pt      % Left margin on even-numbered pages.
\marginparwidth 0.75 true in    % Width of marginal notes.
\oddsidemargin  0 true in       % Note that \oddsidemargin=\evensidemargin
\evensidemargin 0 true in
\topmargin -0.75 true in        % Nominal distance from top of page to top of\textheight 9.5 true in         % Height of text (including footnotes and figures)
\textwidth 6.375 true in        % Width of text line.
\parindent=0pt                  % Do not indent paragraphs
\parskip=0.15 true in
\usepackage{color}              % Need the color package
\usepackage{epsfig}
 

\begin{document}              

\begin{center}
\section*{\underline{WIKI COMPONENT DIAGRAM}}
                            
                            Author Name : Manvendra Baghel
\end{center}
\begin{center}
\input{UseCase_Wiki.latex}
\end{center}
\subsection*{\underline{CREATE PAGE}}
\begin{enumerate}
\item Interact with web application.
\item Sending request to create page.
\item Check for reserved character in page name file should not end be named as brihaspati should not end with ',v' or ',m'.
\item Check for space in the name there should be no space in the file name.
\item Check if file already exist.
\item If success create page and enter version number author, date in Log.
\item If failure send appropriate error message.
\begin{center}
\input{CreatePage_Wiki.latex}
\label{figure:CreatePage_Wiki.latex}
\end{center}
\end{enumerate}
\subsection*{\underline{EDIT PAGE}}
\begin{enumerate}
\item Interact with web application.
\item Sending request to Edit page.
\item Check if edit has been called from a searched page. If yes then we would return with searched results back on page.
\item Check if file is disabled for editing.
\item Check if edited page and original have some difference or not.
\item If success do checking and store the page in RCS and write to log.
\item If failure, send appropriate error message.
\begin{center}
\input{EditPage_Wiki.latex}
\label{figure:EditPage_Wiki.latex}
\end{center}
\end{enumerate}
\subsection*{\underline{VIEW LOG OF PAGE}}
\begin{enumerate}
\item Interact with web application.
\item Sending request to view log file of page.
\begin{center}
\input{Viewlog.latex}
\end{center}
\end{enumerate}
\subsection*{\underline{CONTROL WIKI}}
\begin{enumerate}
\item Interact with web application.
\item Sending request to control the wiki page.
\item ACL check (check for primary Instructor)
\item If success allow control wiki.
\item If failure do not show link to control wiki.
\begin{center}
\input{Control_Wiki.latex}
\end{center}
\end{enumerate}
\subsection*{\underline{MERGE IN WIKI}}
\begin{enumerate}
\item[{}{}]
 Merge is divided into two parts.
\begin{enumerate}
\item  Merge Now
\item  Merge Done
\end{enumerate}
\begin{enumerate}
\item{Merge Now}
\item[{}{}]
Merge the requested version of page with original page. It creates its own version. Merge result are store in wiki working file.
If the request for merge is next time(that is merge is not done first time on  the page) it merges with previous merged file. 
\item{Merge Done}
\item[{}{}]
Deletes all temparary file and copies the merged file to original file. Also it saves the new original page in its RCS.
\end{enumerate}
\end{enumerate}
\subsection*{\underline{API OF WIKI}}
\begin{enumerate}
\item[{}{}]
actions
\item do log(data,context)\\
 shows the log of a file
\item do Diff history(data,context)\\
 shows the changes in the history folder of wiki\\
(approved page)
\item do Diff(data,context)\\
shows the changes in the pages waiting for approval.
\item do Showhistory(data,context)\\
shows the page according to version number(approval page)
\item do Show(data,context)\\
show the page (waiting for approval)\\
according to version number.
\item do Showoriginal (data,context)\\
show the original page (this will not show 1.1, but the original page which may not remine as 1.1)
\item do Delversion(data,context)\\
deletes the unapproved pages from RCS.
\item do Delpage(data,context)\\
delete entire page from wiki.
\item do Edit(data,context)\\
edit the page.
 \end{enumerate}
\subsection*{\underline{WIKI}}
\begin{enumerate}
\item[{}{}]
\item doCreate(data,context)\\
If create a new page.
\item doFind(data,context)\\
If finds a word in all the visible/approved passes of wiki.  
\item doRevert (data,context)\\
If writer the original file.
\item doFindpage(data,context)\\
If finds the page according to page name.
\item doMergenow(data,context)\\
If merge the original page with given page version or the latest merged page.
\item doMergedone(data,context)\\
If compleate then merge process by deleting the temparary file and changing the original page.
\item doStoptraffic(data,context)\\
If stops the student from editing the page by disabling edit button.
\item doStoptraffic(data,context)\\
If restart the edit button or enable the edit buttion.
\item doConflict(data,context)\\
If saves the temparary merged page.
\item doShowconflict(data,context)\\
If shows the temparary merged page.
\end{enumerate}
\subsection*{\underline{UTILS}}
\begin{enumerate}
\item String getMerge(String,String)\\
Find out if merge is done first time or next time on the page.
\item boolean checkint(String)\\
Check if a given string string can be converted to integer from the String.
\item int getint(String)\\
return the integer from the String.
\item String getVersion(String)\\
Finds out latest version from the log file.
\item boolean checktraffic(String)\\
finds out if a file is disable for edit or not.
\item boolean checkconflict(String)\\
Finds out if page(after merge)has conflicts or not.
\item String getfileVersion (String)\\
Finds latest version through RCS, file,v
\item String getRCSVersion(string,string)
gets RCS,version through checkout command.
\item String get Author(String)\\
gets author of page when you pass filename and wikilog directory.
\item String start process(String,string)\\
This is function that executes a command line string and returns either its output stream or error stream.
\end{enumerate}
\subsection*{\underline{IMPLEMENTATION DETAILS OF FEW API}}
\begin{enumerate}
\item doDiff(data,context)\\
 in action Actually to do diff we require
"rcsdiff -rx.y -rx.z filename"
but this command only shows diff between two versions of same file.
If we want to see diff between all files, we have to put above command in Loop.
But there will be a problem. As response time of server is fixed,so if no. of 
page versions are more then response cannot be achieved within that time. Error will come
"Timeout on server"
So I have shown the RCS file itself.
\item doMergeNow(data,context)\\
Merge is done with original file which may not be version 1.1,
so a new version is made of original file and then merge is done.
\item do Show History (data,context)\\
\end{enumerate} 
Written by :- Rekha Pal 

\end{document}              
