\documentclass{article}
\usepackage{graphicx}
\textheight=8.5in
\textwidth=6.5in
\oddsidemargin=0.0in
\topmargin=0.0in

\input{psfig}
\documentstyle[12pt,bezier,amstex]{article}  % include bezier curves
\renewcommand\baselinestretch{1.0}           % single space
\pagestyle{empty}                            % no headers and page numbers
\oddsidemargin -10 true pt      % Left margin on odd-numbered pages.
\evensidemargin 10 true pt      % Left margin on even-numbered pages.
\marginparwidth 0.75 true in    % Width of marginal notes.
\oddsidemargin  0 true in       % Note that \oddsidemargin=\evensidemargin
\evensidemargin 0 true in
\topmargin -0.75 true in        % Nominal distance from top of page to top of\textheight 9.5 true in
       % Height of text (including footnotes and figures)
\textwidth 6.375 true in        % Width of text line.
\parindent=0pt                  % Do not indent paragraphs
\parskip=0.15 true in
\usepackage{color}              % Need the color package
\usepackage{epsfig}

\input{psfig}           % Capability to place postscript drawings
 
\begin{document}
\begin{center}
\section*{\underline{AUTO-UPDATE DESIGN}}
\end{center}
This file provides Documentation for Auto Update-design
\begin{enumerate}
\item Send a request to update every is days.
\item Check authentication.
\begin{itemize}
\item If true go to next step.\\
 else
\item Get message(1) \&  exit.
\end{itemize}
\item Check the version \&  update.
\begin{itemize}
\item If true go to next step.\\
 else
\item get message(2) \& exit.
\end{itemize}\\
If update success go to next step else,message(3)exit.\\
\item Run all scripts,ant Compile,template if sucess go to next step.
\begin{itemize}
\item eles
message(4)&exit.
\item Set true message(5)  
\begin{autoupdate.latex}
\begin{center}
\input{autoupdate.latex}
\caption{Auto update}
\label{figure:autoupdate}
\end{center}
\end{figure}
\end{enumerate} 
\end{itemize}
\end{enumerate}
\end{enumerate}
\subsection*{\underline{Messages}}
\begin{enumerate}
\item You are not authenticate user.
\item Your System is already update.
\item Some file are Correpted.So update is not compelete.
\item Scripts are not successfully executed so check manually.
\item Your System is update successfully.so reboot your server.
\end{enumerate}
\end{document}
