\documentclass{article}
\textheight=8.5in
\textwidth=6.5in
\oddsidemargin=0.0in
\topmargin=0.0in


\renewcommand\baselinestretch{1.0}           % single space
\pagestyle{empty}                            % no headers and page numbers
\oddsidemargin -10 true pt      % Left margin on odd-numbered pages.
\evensidemargin 10 true pt      % Left margin on even-numbered pages.
\marginparwidth 0.75 true in    % Width of marginal notes.
\oddsidemargin  0 true in       % Note that \oddsidemargin=\evensidemargin
\evensidemargin 0 true in
\topmargin -0.75 true in        % Nominal distance from top of page to top of\textheight 9.5 true in         % Height of text (including footnotes and figures)
\textwidth 6.375 true in        % Width of text line.
\parindent=0pt                  % Do not indent paragraphs
\parskip=0.15 true in
\usepackage{color}              % Need the color package
\usepackage{epsfig}

\begin{document}


\begin{center}
\section*{\underline{Documentation : Local Mail}}
                         Author Name : Chitvesh Dutta, Awadesh Kumar Trivedi\\
This file provides Documentation for Local Mail.
Local Mail is used to send messages between all users registered to Brihaspati.
\end{center}
\begin{center}
\input{LocalMail.latex}
\label{figure:LocalMail.latex}
\end{center}
\subsection*{\underline{Mail Sending}}
    \begin{enumerate}
      \item Firstly use, sends Sender-Id and Subject to Mail-Send table, where Msg-Id is     
       generated for that msg.
      \item The if gets the Msg-id for that Msg from Mail-send.
         \item Then Receiver-id and Read flag = 0 is set the Mail-Receiver table corresponding to          
            that uses.
       \item Msg given by the user is entered in the user/username (Receiver username)/Msg.txt       
             with Msg-Id entered at the top and the top and the bottom if there is previously any 
	      Msg in that files then the new Msg gets appended.
	\item Then if attachment is there in the Mail then in User(Static)/ Username/Attachment
	      (Static) Msg-id/Msg of current-Msg Attached.
	      In this way the file all saved in the folder of the Msg-Id which the Msg got of 
	      which they were attachments.
\begin{center}
\input{Send_Loclmail.latex}
\label{figure:Send_Loclmail.latex}
\end{center}
\end{enumerate}
\subsection*{\underline{Receiving Mail}}
\begin{enumerate}
		\item During Receiving of Mail in the Mail page Mail.vm in table. Mail receive all mails		      are checked and the mail that have Read Flag = 1. So the message information is displayed in the main screen.
\begin{center}
\input{Recv_LoclMail.latex}
\label{figure:Recv_LoclMail.latex}
\end{center}
\end{enumerate}
\subsection*{\underline{To view ACL Message}}
	\begin{enumerate}
        \item First check in Mail-Receiver for the Receiver-Id the uses who is logged on.
	\item Then corresponding to the Receiver-Id get the Msg-Id get the subject and Sender-Id.
	\item From Mail-Send and now display all message in the sorted order of receiving time.
	\end{enumerate}
\subsection*{\underline{Viewing a particular Mail}}
	\begin{enumerate}
	\item For viewing a particular Mail the subject post time and send name, we have already
      Got not we search for the text in Msg.txt of that user and the message between two    
      message Ids is shown in the screen.
	\item For viewing the Attachment we have the Msg. in the Attachments folder if there is a     
      Folder the Attachment file in that folder is displayed in the screen with a link to    
      Download and views the attachment.
	\end{enumerate}
\subsection*{\underline{Deleting Mail}}
	\begin{enumerate}
	\item For deleting a Mail first, we search for that Msg-Id in the Msg.txt of that is deleted   
	      From Msg.txt.
	\item Then we search for Msg-Id in Attachment folder if there is any the file inside the folder   
	      is deleted and then that folder is removed. \\

                                                     Written by :- Rekha Pal
\end{enumerate}
 \end{document}
      
