\documentclass{article}
\textheight=8.5in
\textwidth=6.5in
\oddsidemargin=0.0in
\topmargin=0.0in


\renewcommand\baselinestretch{1.0}           % single space
\pagestyle{empty}                            % no headers and page numbers
\oddsidemargin -10 true pt      % Left margin on odd-numbered pages.
\evensidemargin 10 true pt      % Left margin on even-numbered pages.
\marginparwidth 0.75 true in    % Width of marginal notes.
\oddsidemargin  0 true in       % Note that \oddsidemargin=\evensidemargin
\evensidemargin 0 true in
\topmargin -0.75 true in        % Nominal distance from top of page to top of\textheight 9.5 true in
       % Height of text (including footnotes and figures)
\textwidth 6.375 true in        % Width of text line.
\parindent=0pt                  % Do not indent paragraphs
\parskip=0.15 true in
\usepackage{color}              % Need the color package
\usepackage{epsfig}

\begin{document}


\begin{center}
\section*{\underline{Documentation: Admin Functionality's}}
      Author Name : Madhavi 
\end{center}
This file provides Documentation for Admin Functionality's.
\begin{enumerate}
\item Adding a new course-creation of course profile.
\item Adding user  (and his profile).
\item Modify course profile.
\item Modify user profile.
\item Modify user role in course.
\item Remove course - profile and course.
\item Remove user - profile.
\item Giving a role to in user in a course.
\item Removing role of user in a course.
\item List course.
\item List users.
\item List content authors.
\item Login as an instructors.
\item Managing contents backup \& restoration.                                  
\item Change own password and profile.
\item Setting configuration parameters (what configuration parameter).
\item Send notices.
\item Remove notices (any  body).
\item Add general / course news.
\item Modify general / course news (put up by any body).
\item Remove general / course news  (put up by any body).
\item Backup (data base /content).
\item Restore (data base/ content).
\item Adds words to glossary.
\item Remove words from glossary (created by any body).
\item Modify words in glossary (created by any body).
\item Add remove content author status to and user.
\item Managing content repository /contents.
\item Request for the registration of new course with primary instructor 'user'.
\item Check if the course exits with user as instructor.
\item If exits send error that course emit with user as instructor.
\item Else current course profile and send request to give role to user as instructor.
\item If user already emit give him role and send success message.
\item If user does not exist , create user and give him role. Send message that new user created.
\end{enumerate}
\subsection*{\underline{REGISTERING A SECORDRY INSTRUCTOR /STUDENT}}
Send request for registry a user as recordry instructor /student.
\subsection*{\underline{Check if user exist-if yes}}
\begin{enumerate}
\item Find its role in course.
\item If (student and requested role = instructor).
\item If (student and requested role = instructor).
\item If (instructor) send error message that user is already having role as instructor.
\item Else creates new course and give him the requested role. 
\end{enumerate}
\subsection*{\underline{Modify Course}}
\begin{enumerate}
\item Give the course details for updation.
\item Update all the tables related to the particular course.
\item Give back the appropriate message.
\begin{center}
\input{admin_ModifyCourse.latex}
\end{center}
\end{enumerate}
\subsection*{\underline{Modify User/Role}}
\begin{enumerate}
\item Send the user for whom updation has to be done.
\item If want to modify role of the user then get the course-list as well as the role in the same for the user.
\item Some the updated role/data for user.
\item Give back the appropriate message.
\end{enumerate}
\begin{center}
\input{admin_ModifyUser_Role.latex}
\end{center}
\subsection*{\underline{Remove Course}}
\begin{enumerate}
\item Send the course name for removal.
\item Checks if the course is active/inactive.
\item If active , return error message.
\item If inactive get the list of all user registered in this course.
\item Remove the role of user from this course and remove orphan users too.
\item Return the result.
\item If (5) return success then remove the course entries from database and remove directory structure. 
\item If (5) return any error then restore all the removal actions performed earlier with error message.
\item If (6) is successful /then return appropriate message. 
\item If (6) is not successful , return appropriate error message.
\end{enumerate}

\begin{center}
\input{admin_RemoveCourse.latex}
\end{center}
\subsection*{\underline{Removing Users Profile}}
\begin{enumerate}
\item Request to remove users profile.
\item Get all the course where the user is student.
\item Remove the users role from the course obtained in step.
\item Get all the courses where the user is an instructor.
\item Pass the list of courses obtained in step (4), and check for primary instructor.
\item For each of the inactive courses in step (5), get the list of inactive courses.
\item For each of the inactive courses in step (6).
\item Get the list of all the user who are students . Remove their roles from the course . Check for orphan user.
\item Get the list of all the user who are instructor . Remove their roles from the course. Check for orphan user.
\item Remove the course directory . Remove the course entry from data base.
\item For all the courses in step (4) except the courses in step (6) , remove the use role from the course.
\item Return appropriate message.
\begin{center}
\input{admin_RemovingUser_profile.latex}
\end{center}
\subsection*{\underline{Removing User Role From a group}}
\begin{enumerate}
\item Send the username + course name which the users role has to be removed.
\item Get the role of user in the course.
\item If the user is a student , then remove his role from the course and give back appropriate message.
\item If the user is an instructor , check if he is a primary instructor 
\item If yes (user in primary instructor ) then send back the status of course (active \& inactive ) along with course name. 
\item If inactive , then get list of all the students and instructor in the course and remove their roles from the course. Remove the course directory and course entries from the database.
\item If active, then give back the error message.  
\item If no (user is not primary instructor) then remove his role from the course and give back appropriate message.

\begin{center}
\input{admin_RemovingUser_rolefrom.latex}
\end{center}
\end{enumerate}
\end{enumerate} 

Written by:- Rekha Pal
\end{document}
